A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-31 writeup/paper.tex
Cropped and moved the Google match figure.
Fixed typos

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5.2cm}    % Expanding the titlebox

@@

There are several complicating factors when trying to take a census of workers on MTurk.  The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.  Posting a simple survey to have workers self-report this information may be inadequate, since (a) many workers may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.

@@

Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.  \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese, Hindi, Telugu, Urdu, and Haitian Creole.  In a study of 2000 Urdu sentences, 
\newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence. 
\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.  \newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic machine translation on verb-final languages.  
Several researchers have examined cost optimization using active learning techniques to select the most useful sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.

@@

We drew our data from the different language versions of Wikipedia.   We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages, giving a total of 119 languages (Table \ref{wikipedia-buckets}). For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from each. The resulting vocabularies served as the input to our translation HIT.

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=0.8\linewidth]{final-figures/google-match}
\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
\label{googlematch} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For the translation task, we asked Turkers to translate individual words.  We showed each word in the context of three sentences that were drawn from Wikipedia.  
Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.   
We gave special instruction for translating names of people and places, giving examples of how to handle `Barack Obama' and `Australia' using their interlanguage links. For languages with non-Latin alphabets, names were transliterated.

@@

We calculate the quality of translations on the level of individual assignments and aggregated over languages and countries.  We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
\begin{align}	
	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
\end{align}	
where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true. 
Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.

@@

@@

Figure \ref{completion-time} gives the completion times for 40 languages.  
Workers for Urdu and Russian HITs responded almost immediately; workers in the other languages began slightly later. The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi. 7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.  Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{figure*}
\footnotesize
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

We used Google Translate to translate all 10,000 words for 50 foreign languages that Google Translate covers. We measured the percent of translations received that exactly matched the translation returned from Google translate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with Google translate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

@@

\paragraph{Validation of controls} 
Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some of the control translations used may have been already indexed by Google. We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.

As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries. Turkers' performance on our control tasks is well correlated with this measure of quality.    We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between en and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz. }  We used each of these bilingual dictionaries to computer language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.  In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.

We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.53$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.

>>>>

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5cm}    % Expanding the titlebox

@@

There are several complicating factors when trying to take a census of workers on MTurk.  The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.  Posting a simple survey to have workers report this information may be inadequate, since (a) many workers may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.

@@

Several researchers have investigated using MTurk to build bilingual parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.  \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese, Hindi, Telugu, Urdu, and Haitian Creole.  In a study of 2000 Urdu sentences, 
\newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence. 
\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.  \newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic machine translation on verb-final languages.  
Several researchers have examined cost optimization using active learning techniques to select the most useful sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.

@@

We drew our data from the different language versions of Wikipedia.   We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 low resource languages, giving a total of 119 languages (Table \ref{wikipedia-buckets}). For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them. The resulting vocabularies served as the input to our translation HIT.

@@

@@

For the translation task, we asked Turkers to translate individual words.  We showed each word in the context of three sentences that were drawn from Wikipedia.  
Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and 2 of which were quality control words with known translations.   
We gave special instruction for translating names of people and places, giving examples of how to handle `Barack Obama' and `Australia' using their interlanguage links. For languages with non-Latin alphabets, names were transliterated.

@@

We calculate the quality of translations on the level of individual assignments and aggregated over languages and countries.  We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous or related.
\begin{align}	
	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
\end{align}	
where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true. 
Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.

@@

Figure \ref{completion-time} gives the completion times for 40 languages.  
The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi. 7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.  Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\footnotesize
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1\linewidth]{final-figures/google-match}
\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
\label{googlematch} 
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We used Google Translate to translate all 10,000 words for 50 foreign languages that Google Translate covers. We measured the percent of translations received that exactly matched the translation returned from Google translate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with Google translate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

@@

\paragraph{Validation of controls} 
Higher overlap with Google translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.22), suggesting that some control translations have already been indexed by Google. We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.

As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries. Turkers' performance on our control tasks is well correlated with this measure of quality.    We had external bilingual dictionaries for 27 of the 119 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz. }  We used each of these bilingual dictionaries to computer language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.  In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.

We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.53$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
